An Integrated Framework for Robust Estimation, Prediction and Control

### 2019-12-20 main.tex
Updates from Overleaf

\begin{proposition}
We can enclose the confidence ellipsoid $C_\delta$ obtained in $\eqref{eq:confidence-ellipsoid}$ within a polytope $P_\delta$:
\[\cC_\delta \subset \cP_\delta\]
where $\cP_\delta$ can be written as:
\begin{equation}
     \cP_\delta = \left\{ A_{0}+\sum_{i=1}^{2^d}\lambda_{i}\Delta A_{i}: \lambda\in[0, 1]^{2^d},  \sum_{i=1}^{2^d}\lambda_{i}=1\right\}.
\end{equation}
with 
\begin{align*}
    &G_{N,\lambda}^{-1} = PDP^{-1}\\
    &h_k \text{ is the }k^\text{th}\text{ element of }\{-1,1\}^d\text{, for } k\in[2^d]\\
    &\Delta\theta_k = 2 C_{n,\lambda,\delta}^{1/2} P^{-1}D^{-1/2} h_k \\
    &A_0 = \theta_{N,\lambda}^T\Phi\\
    &\Delta A_k = \Delta\theta_k^T\Phi\\
\end{align*}
\end{proposition}

>>>>

\begin{proposition}
We can enclose the confidence ellipsoid $C_\delta$ obtained in $\eqref{eq:confidence-ellipsoid}$ within a polytope $P_\delta$:
\[\cC_\delta \subset \cP_\delta\]
where $\cP_\delta$ can be written as:
\begin{equation}
     \cP_\delta = \left\{ A_{0}+\sum_{i=1}^{2^d}\lambda_{i}\Delta A_{i}: \lambda\in[0, 1]^{2^d},  \sum_{i=1}^{2^d}\lambda_{i}=1\right\}.
\end{equation}
with 
\begin{align*}
    &G_{N,\lambda}^{-1} = PDP^{-1}\\
    &h_k \text{ is the }k^\text{th}\text{ element of }\{-1,1\}^d\text{, for } k\in[2^d]\\
    &\Delta\theta_k = C_{N,\lambda,\delta}^{1/2} P^{-1}D^{-1/2} h_k \\
    &A_0 = \theta_{N,\lambda}^T\Phi\\
    &\Delta A_k = \Delta\theta_k^T\Phi\\
\end{align*}
\end{proposition}
\begin{proof}
The ellipsoid in \eqref{eq:confidence-ellipsoid} is described by:
\begin{align*}
    \theta\in\cC_\delta &\implies
    (\theta-\theta_{N,\lambda})^T G_{N,\lambda}^{-1}(\theta-\theta_{N,\lambda}) \leq C_{N,\lambda,\delta}\\
    &\implies (\theta'-\theta'_{N,\lambda})^T D (\theta'-\theta'_{N,\lambda}) \leq C_{N,\lambda,\delta}\\
    &\implies \sum_{i=1}^d D_{i,i}(\theta'_i-\theta'_{N,\lambda,i})^2\leq C_{N,\lambda,\delta}\\
    &\implies\forall i, |\theta'_i-\theta'_{N,\lambda,i}|\leq C_{N,\lambda,\delta}^{1/2}D_{i,i}^{-1/2}
\end{align*}
This describes a $\Real^d$ box containing $\theta' = P\theta$, whose $k^\text{th}$ vertex is represented by $\theta_{N,\lambda}' + C_{N,\lambda,\delta}^{1/2}D^{-1/2} h_k$. We obtain the corresponding box on $\theta$ by transforming each vertex of the box with $P^{-1}$.
\end{proof}
